formula1

### 2020-06-09 inst/f1points.Rmd
label all chunks and more samples

```{r,echo=FALSE,print=FALSE}
library(hyper2,quietly=TRUE)
top <- 11
H <- ordertable2supp(F1_table_2017[seq_len(top),])
head(H,5)
```

@@

```{r,echo=FALSE}
mH <- maxp(H)
print(mH)
pie(maxp(H)[c(1,6,11,2,7,3,8,4,9,5,10)])
```

@@

```{r,cache=TRUE}
samep.test(H,1:2)
```

@@

```{r,label=calcpoints,echo=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

```{r,montecarlosetup, echo=FALSE, cache=FALSE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
#m <- maxp(ordertable2supp(as.ordertable(f2017)))

@@

```{r,montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))

points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)

o1 <- replicate(100,resampling(m,f2017,points=points1))
plot(table(o1))

o2 <- replicate(100,resampling(m,f2017,points=points2))
plot(table(o2))

table(o1)
table(o2)
```

>>>>

```{r,label=showanordertableandhead,echo=FALSE,print=FALSE}
library(hyper2,quietly=TRUE)
top <- 11
H <- ordertable2supp(F1_table_2017[seq_len(top),])
head(H,5)
```

@@

```{r,label=printapiechart,echo=FALSE}
mH <- maxp(H)
print(mH)
pie(maxp(H)[c(1,6,11,2,7,3,8,4,9,5,10)])
```

@@

```{r,label=dosameptest,cache=TRUE}
samep.test(H,1:2)
```

@@

```{r,label=calcpoints,echo=TRUE,cache=TRUE}
p <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
dp <- ordertable2points(as.ordertable(F1_table_2017[seq_len(top),]),p)
dp <- sort(dp,decreasing=TRUE)
dp[] <- seq_along(dp)
m <- maxp(H)
m <- sort(m,decreasing=TRUE)
m[] <- seq_along(m)
```

@@

```{r,label=montecarlosetup, echo=FALSE, cache=FALSE}
top <- 11
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
#m <- maxp(ordertable2supp(as.ordertable(f2017)))

@@

```{r,label=montecarlosetup2, cache=TRUE}
f2017 <- read.table("formula1_2017.txt",header=TRUE)[seq_len(top),1:20]
m <- maxp(ordertable2supp(as.ordertable(f2017)))
points1 <- c(25, 18, 15, 12, 10, 8, 6, 4, 2, 1, 0, 0)
points2 <- c(1, 0,0,0,0)
points3 <- c(1, 1,1,1,1,1,0,0,0,0,0)
```

```{r,label=montecarlo_doer1, cache=TRUE}
o1 <- replicate(1000,resampling(m,f2017,points=points1))
```

```{r,label=montecarlo_doer2, cache=TRUE}
o2 <- replicate(1000,resampling(m,f2017,points=points2))

```{r,label=montecarlo_doer3, cache=TRUE}
o3 <- replicate(1000,resampling(m,f2017,points=points3))
```

```{r,label=montecarlo_shower}
plot(table(o1))
plot(table(o2))
plot(table(o3))

table(o1)
table(o2)
table(o3)

mean(o1)
mean(o2)
mean(o3)

M <- rbind(tabulate(o1+1),tabulate(o2+1),tabulate(o3+1))
dimnames(M) <- list(system=LETTERS[1:3],correct=0:11)
M
```

```{r}
out <- data.frame(rbind(cbind("A",o1),cbind("B",o2),cbind("C",o3)))
colnames(out) <- c("system","correct")
head(out)
tail(out)
summary(lm(correct~system,data=out))
```
